\documentclass{article}

\thispagestyle{empty}

\begin{document}
Hello David, Jason, and everyone at 37signals,
\newline

My name is Dorian Marié, I'm a programmer since I started at 12 years old (now I'm 32 years old, so 20 happy years of programming).
\newline

Started with a bit of C, a lot of C++, years of PHP/SQL/HTML/CSS, then discovered Rails in 2020 (at 18 years old) and felt in love with Rails and Ruby.
\newline

I started rewriting a project I made in PHP in two weeks (a simple question / answer) and made it in one day with Ruby and Rails. I was impressed so I decided to rewrite my school's student's website in Rails.
\newline

In two weeks I made more progress than a team of 4 in 6 months doing it in PHP. So I trained the team in Ruby and Rails and we did it in Rails.
\newline

Having accumulated some experience with Ruby and Rails I found a 6 months internship in New York at Bespoke Post. That internship went well and we decided to keep working together.
\newline

After 2 years of working at Bespoke Post I decided to go back to school, then found an internship in San Francisco at Trusted for 6 months. Still in Ruby and Rails.
\newline

Then I worked at Doctolib, the biggest french healhcare startup, and thoughtbot that you know of.
\newline

Now I work at Workelo, an onboarding/crossboarding/offboarding company for employees of large companies.
\newline

But since I discovered 37signals, Basecamp, Hey, DHH, Jason Fried, and all the Basecamp culture I always dreamed of working at 37signals.
\newline

And I think now is a good time, I made my contributions to github.com/rails/rails and related gems
\newline

My personal project is a programming language named Code available at codedorian.com. I only have 7 users but it's making me happy to work on it in my spare time.
\newline

Hoping we get to get in touch and make great things together
\newline

Dorian
\newline
\end{document}

